Transfer report

### 2018-09-21 Report/paper-all-data.Rmd
Updates the report

source("../Scripts/loading.R")
source_folder("../TwoWorlds")
source('../Scripts/analysis-helpers.R')
sop_all <- read.table("../sop.csv", sep=";", header = T, stringsAsFactors = F)
walk_all <- read.table("../walk.csv", sep=";", header = T, stringsAsFactors = F)
walk_all$learning.condition <- walk_all$condition
walk_all$learning.condition <- recode(walk_all$learning.condition, "real-real" = "Real", "ve-real" = "Desktop", "vr-real" = "Treadmill VR", "real-vr" = "Real", "vr-vr" = "Treadmill VR")
sop_all$learning.condition <- sop_all$condition
sop_all$testing.condition <- sop_all$condition
sop_all$learning.condition <- recode(sop_all$learning.condition, "real-real" = "Real", "ve-real" = "Desktop", "vr-real" = "Treadmill VR", "real-vr" = "Real", "vr-vr" = "Treadmill VR")
sop_all$testing.condition <- recode(sop_all$testing.condition, "real-real" = "Real", "ve-real" = "Real", "vr-real" = "Real", "real-vr" = "Treadmill VR", "vr-vr" = "Treadmill VR")

conference_walk_all <- walk_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))
conference_sop_all <- sop_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))

#green, violet, blue, yellow, pink, dark blue
estimote_pal <- c('#b6d6c1', '#54003d','#93d5f6','#d5d215','#f3aacb','#2d2556')
theme_set(theme_minimal())
```

## Per phase separation
```{r warning=F, echo=F}
make_graph(conference_walk_all, "learning.condition", "distance", "phase") + 
  ylab("Average absolute trial distance") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal,"Phase")

make_graph(conference_walk_all, "learning.condition", "min_norm_distance", "phase") + 
  ylab("Average normalised trial distance") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal,"Phase")

make_graph(conference_walk_all, "learning.condition", "time", "phase") + 
  ylab("Average absolute trial duration") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal,"Phase")

make_graph(conference_walk_all, "learning.condition", "min_norm_time", "phase")+ 
  ylab("Average normalised trial duration") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal, "Phase")

make_graph(conference_walk_all, "learning.condition", "errors", "phase")+ 
  ylab("Average number of errors") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal,"Phase")
```

## PER BLOCK
```{r warning=F, echo=F}
make_graph(conference_walk_all, "learning.condition", "distance", "exp_block_id") + 
  ylab("Average absolute trial distance") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F)

make_graph(conference_walk_all, "learning.condition", "min_norm_distance", "exp_block_id") + 
  ylab("Average normalised trial distance") +  xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F)

make_graph(conference_walk_all, "learning.condition", "time", "exp_block_id") + 
  ylab("Average absolute trial duration") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F)

make_graph(conference_walk_all, "learning.condition", "min_norm_time", "exp_block_id") + 
  ylab("Average normalised trial duration") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F)

make_graph(conference_walk_all, "learning.condition", "errors", "exp_block_id")+ 
  ylab("Average number of errors") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F)

ggplot(conference_walk_all, aes(x = exp_block_id, y = min_norm_distance, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 3.5, linetype=4) +
  ylab("Average normalised trial distance") + xlab("Block") + 
  scale_color_manual(values=estimote_pal,"Condition") + guides(fill=F)

ggplot(conference_walk_all, aes(x = exp_trial_id, y = min_norm_distance, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 18.5, linetype=4) +
  ylab("Average normalised trial distance") + xlab("Block number") + 
  scale_color_manual(values=estimote_pal, "Condition")

ggplot(conference_walk_all, aes(x = exp_block_id, y = errors, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 3.5, linetype=4) +
  ylab("Number of mistakes in office decision") + xlab("Block number") + 
  scale_color_manual(values=estimote_pal, "Condition")

@@

# Block measures
```{r, echo = F}
condition_all_sums <- conference_walk_all %>% 
  group_by(exp_block_id, id, learning.condition) %>% 
  summarise(sum.distance = sum(min_norm_distance, na.rm = T), 
            sum.errors = sum(errors, na.rm = T),
            mean.distance = mean(min_norm_distance, na.rm = T),
            mean.error = mean(errors, na.rm = T))

@@

## Sum of errors
Measure of overall sum of errors. Mean columns define mean sum of errors for all participants in that block
```{r, echo=F, warnings = F}
df <- block_measure(condition_all_sums, "sum.errors")
kable(df)
ggplot(melt(df[,1:4]), aes(x = learning.condition, y = value, fill = variable)) + 
  geom_bar(stat = 'identity', position="dodge") + 
  scale_fill_manual(values = estimote_pal) +
  ylab("Mean sum of errors") + xlab("Learning condition")  + guides(fill=F)

@@

### Block 3-4
Paired t tests between min normalised distance difference in blocks 3 and 4.
```{r, echo=F}
kable(block_t_test(conference_walk_all, 4, 3,"min_norm_distance"))
```

And for number of errors
```{r, echo=F}
kable(block_t_test(conference_walk_all, 4, 3,"errors"))
```

### Block 1-4
Paired t tests between min normalised distance difference in blocks 1 and 4.
```{r, echo=F}
kable(block_t_test(conference_walk_all, 4, 1,"min_norm_distance"))
```
And for number of errors
```{r, echo=F}
kable(block_t_test(conference_walk_all, 4, 1,"errors"))
```

@@

```{r, echo=F}
kable(block_t_test(conference_walk_all, 6, 1,"min_norm_distance"))
```

@@

```{r, echo=F}
kable(block_t_test(conference_walk_all, 6, 1,"errors"))
```

@@

## Anova
Simple between subjects anova
```{r, echo=F}
aov_block_distance <- aov(min_norm_distance~exp_block_id*learning.condition, conference_walk_all)
kable(anova_table(aov_block_distance))
```

@@

clean_walk_14 <- ez_prepare_block(conference_walk_all, c(1,4))
clean_walk_34 <- ez_prepare_block(conference_walk_all, c(3,4))
```

>>>>

source("../Scripts/paper-prepare.R")

#green, violet, blue, yellow, pink, dark blue
estimote_pal <- c('#b6d6c1', '#54003d','#93d5f6','#d5d215','#f3aacb','#2d2556')
estimote_pal_mono <- function(n){return(rep(estimote_pal[n],6))}
theme_set(theme_minimal())
```

## Per phase separation
```{r warning=F, echo=F}
make_graph(sub_walk_all, "learning.condition", "distance", "phase") + 
  ylab("Average absolute trial distance") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal,"Phase")

make_graph(sub_walk_all, "learning.condition", "min_norm_distance", "phase") + 
  ylab("Average normalised trial distance") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal,"Phase")

make_graph(sub_walk_all, "learning.condition", "time", "phase") + 
  ylab("Average absolute trial duration") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal,"Phase")

make_graph(sub_walk_all, "learning.condition", "min_norm_time", "phase")+ 
  ylab("Average normalised trial duration") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal, "Phase")

make_graph(sub_walk_all, "learning.condition", "errors", "phase")+ 
  ylab("Average number of errors") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal,"Phase")
```

## PER BLOCK
```{r warning=F, echo=F}
make_graph(walk_all, "learning.condition", "distance", "exp_block_id") + 
  ylab("Average absolute trial distance") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F)

make_graph(sub_walk_all, "learning.condition", "min_norm_distance", "exp_block_id") + 
  ylab("Average normalised trial distance") +  xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F)

make_graph(sub_walk_all, "learning.condition", "time", "exp_block_id") + 
  ylab("Average absolute trial duration") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F)

make_graph(sub_walk_all, "learning.condition", "min_norm_time", "exp_block_id") + 
  ylab("Average normalised trial duration") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F)

make_graph(sub_walk_all, "learning.condition", "errors", "exp_block_id")+ 
  ylab("Average number of errors") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F)

ggplot(sub_walk_all, aes(x = exp_block_id, y = min_norm_distance, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 3.5, linetype=4) +
  ylab("Average normalised trial distance") + xlab("Block") + 
  scale_color_manual(values=estimote_pal,"Condition") + guides(fill=F)

ggplot(sub_walk_all, aes(x = exp_trial_id, y = min_norm_distance, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 18.5, linetype=4) +
  ylab("Average normalised trial distance") + xlab("Block number") + 
  scale_color_manual(values=estimote_pal, "Condition")

ggplot(sub_walk_all, aes(x = exp_block_id, y = errors, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 3.5, linetype=4) +
  ylab("Number of mistakes in office decision") + xlab("Block number") + 
  scale_color_manual(values=estimote_pal, "Condition")

@@

# Block measures
```{r, echo = F}
condition_all_sums <- sub_walk_all %>% 
  group_by(exp_block_id, id, learning.condition) %>% 
  summarise(sum.distance = sum(min_norm_distance, na.rm = T), 
            sum.errors = sum(errors, na.rm = T),
            mean.distance = mean(min_norm_distance, na.rm = T),
            mean.error = mean(errors, na.rm = T))

@@

## Sum of errors

Measure of overall sum of errors. Mean columns define mean sum of errors for all participants in that block
```{r, echo=F, warnings = F}
df <- block_measure(condition_all_sums, "sum.errors")
kable(df)
ggplot(melt(df[,1:4]), aes(x = learning.condition, y = value, fill = variable)) + 
  geom_bar(stat = 'identity', position="dodge") + 
  scale_fill_manual(values = estimote_pal) +
  ylab("Mean sum of errors") + xlab("Learning condition")  + guides(fill=F)

@@

### Block 3-4
Paired t tests between min normalised distance difference in blocks 3 and 4.
```{r, echo=F}
kable(block_t_test(sub_walk_all, 4, 3,"min_norm_distance"))
```

And for number of errors
```{r, echo=F}
kable(block_t_test(sub_walk_all, 4, 3,"errors"))
```

### Block 1-4
Paired t tests between min normalised distance difference in blocks 1 and 4.
```{r, echo=F}
kable(block_t_test(sub_walk_all, 4, 1,"min_norm_distance"))
```
And for number of errors
```{r, echo=F}
kable(block_t_test(sub_walk_all, 4, 1,"errors"))
```

@@

```{r, echo=F}
kable(block_t_test(sub_walk_all, 6, 1,"min_norm_distance"))
```

@@

```{r, echo=F}
kable(block_t_test(sub_walk_all, 6, 1,"errors"))
```

@@

## Anova
Simple between subjects anova
```{r, echo=F}
aov_block_distance <- aov(min_norm_distance~exp_block_id*learning.condition, sub_walk_all)
kable(anova_table(aov_block_distance))
```

@@

clean_walk_14 <- ez_prepare_block(sub_walk_all, c(1,4))
clean_walk_34 <- ez_prepare_block(sub_walk_all, c(3,4))
```

### 2018-09-21 Report/paper-story.Rmd
Updates the report

source("../Scripts/loading.R")
source_folder("../TwoWorlds")
source('../Scripts/analysis-helpers.R')
sop_all <- read.table("../sop.csv", sep=";", header = T, stringsAsFactors = F)
walk_all <- read.table("../walk.csv", sep=";", header = T, stringsAsFactors = F)
walk_all$learning.condition <- walk_all$condition
walk_all$learning.condition <- recode(walk_all$learning.condition, "real-real" = "Real", "ve-real" = "Desktop", "vr-real" = "Treadmill VR", "real-vr" = "Real", "vr-vr" = "Treadmill VR")
sop_all$learning.condition <- sop_all$condition
sop_all$testing.condition <- sop_all$condition
sop_all$learning.condition <- recode(sop_all$learning.condition, "real-real" = "Real", "ve-real" = "Desktop", "vr-real" = "Treadmill VR", "real-vr" = "Real", "vr-vr" = "Treadmill VR")
sop_all$testing.condition <- recode(sop_all$testing.condition, "real-real" = "Real", "ve-real" = "Real", "vr-real" = "Real", "real-vr" = "Treadmill VR", "vr-vr" = "Treadmill VR")

conference_walk_all <- walk_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))
conference_sop_all <- sop_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))

#green, violet, blue, yellow, pink, dark blue
estimote_pal <- c('#b6d6c1', '#54003d','#93d5f6','#d5d215','#f3aacb','#2d2556')
theme_set(theme_minimal())

condition_all_sums <- conference_walk_all %>% 
  group_by(exp_block_id, id, learning.condition) %>% 
  summarise(sum.distance = sum(min_norm_distance, na.rm = T), 
            sum.errors = sum(errors, na.rm = T),
            mean.distance = mean(min_norm_distance, na.rm = T),
            mean.error = mean(errors, na.rm = T))

block_measure <- function(df, value){
  df_wide <- dcast(df, learning.condition + id ~ exp_block_id, value.var = value)
  colnames(df_wide) <- c("learning.condition","id","block1", "block2","block3","block4","block5","block6")
  df_wide %>% 
    group_by(learning.condition) %>%
    summarise(block1.mean  = mean(block1, na.rm = T),
              block3.mean = mean(block3, na.rm = T),
              block4.mean = mean(block4, na.rm = T),
              block34.diff = mean((block3-block4)/(block4+block3), na.rm = T),
              block34.se  = sqrt(var((block3-block4)/(block4+block3), na.rm = T)/sum(!is.na(block3-block4))),
              block14.diff = mean((block1-block4)/(block1+block4), na.rm = T),
              block14.se = sqrt(var((block1-block4)/(block1+block4), na.rm = T)/sum(!is.na(block1-block4)))
  )
}

@@

I ran all tests on the normalised distance, errors are not normalised, as they are the same in all conditions.

I only selected those "important" comparisons - therefore Desktop to Real world, Treadmill VR to real world and Real world to real world. Anovas and other comparisons are run only on these. Learning conditions (block 1-3) are the different modalities, and blocks 3-4 are all real world testing.

## Descriptives
In normalised distance we can see that people in different conditions start fairly at the same level of performance (difference between learnign conditions is not significant `r apa_print(aov(min_norm_distance ~ learning.condition, conference_walk_all[conference_walk_all$exp_block_id == 1, ]))$statistic$learning_condition`)

```{r, echo=F, warning=F}
make_graph(conference_walk_all, "learning.condition", "min_norm_distance", "exp_block_id") + 
  ylab("Average normalised trial distance") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal,"Block ID")

ggplot(conference_walk_all, aes(x = exp_block_id, y = min_norm_distance, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 3.5, linetype=4) +
  ylab("Average normalised trial distance") + xlab("Block") + 
  scale_color_manual(values=estimote_pal,"Condition") + guides(fill=F)
```

There is difference in normalised times in all conditions in the first block (`r apa_print(aov(min_norm_time ~ learning.condition, conference_walk_all[conference_walk_all$exp_block_id == 1, ]))$statistic$learning_condition`)). Probably due to learning issues with the treadmill. Threre is no significant difference between desktop and real world learning in normalised times (`r apa_print(t.test(min_norm_time ~ learning.condition, conference_walk_all[conference_walk_all$exp_block_id == 1 & conference_walk_all$learning.condition %in% c("Desktop", "Real"), ]))$statistic`))

```{r, echo=F}
make_graph(conference_walk_all, "learning.condition", "min_norm_time", "exp_block_id")+ 
  ylab("Average normalised trial duration") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal, "Block ID")
```

And we don't have any significant difference in number of errors in the first block (`r apa_print(aov(errors ~ learning.condition, conference_walk_all[conference_walk_all$exp_block_id == 1, ]))$statistic$learning_condition`)).

```{r, echo=F}
make_graph(conference_walk_all, "learning.condition", "errors", "exp_block_id")+ 
  ylab("Average number of errors") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal," Block ID")

ggplot(conference_walk_all, aes(x = exp_block_id, y = errors, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 3.5, linetype=4) +
  ylab("Number of mistakes in office decision") + xlab("Block number") + 
  scale_color_manual(values=estimote_pal, "Condition")
```

We can clearly see differences in the progression of the learning slopes, but as you pointed out many times, as they are not linear, we could benefit from non linear modeling. I hope Mike and professor Ferer will help us with that.

@@

clean_walk_14 <- ez_prepare_block(conference_walk_all, c(1,4))
clean_walk_34 <- ez_prepare_block(conference_walk_all, c(3,4))
```

## Block improvement from block 1 to block 4

### Distance
All conditions improved from the first to fourth block in both distance walked and errors in decisions. Paired t-tests show that both Treadmill and Real world learning conditions led to improved performance from 1-4, but Desktop did not. All conditions show significant improvement in number of errors from block 1 to 4.

```{r, echo=F}
df_dist <- block_t_test(conference_walk_all, 1, 4,"min_norm_distance")[,c(1,4)]
df_error <- block_t_test(conference_walk_all, 1, 4,"errors")[,c(1,4)]
df14 <- merge(df_dist, df_error, by = "learning.condition")
colnames(df14) <- c("learning condition", "p-value distance improvement", "p-value errors improvement")
kable(df14)
```

@@

```{r, echo=F}
df_dist <- block_t_test(conference_walk_all, 3, 4,"min_norm_distance")[,c(1,4)]
df_error <- block_t_test(conference_walk_all, 3, 4,"errors")[,c(1,4)]
df34 <- merge(df_dist, df_error, by = "learning.condition")
colnames(df34) <- c("learning.condition", "p-value distance improvement", "p-value errors improvement")
kable(df34)
```

>>>>

source("../Scripts/paper-prepare.R")
#green, violet, blue, yellow, pink, dark blue
estimote_pal <- c('#b6d6c1', '#54003d','#93d5f6','#d5d215','#f3aacb','#2d2556')
theme_set(theme_minimal())

condition_all_sums <- sub_walk_all %>% 
  group_by(exp_block_id, id, learning.condition) %>% 
  summarise(sum.distance = sum(min_norm_distance, na.rm = T), 
            sum.errors = sum(errors, na.rm = T),
            mean.distance = mean(min_norm_distance, na.rm = T),
            mean.error = mean(errors, na.rm = T))

block_measure <- function(df, value){
  df_wide <- dcast(df, learning.condition + id ~ exp_block_id, value.var = value)
  colnames(df_wide) <- c("learning.condition","id","block1", "block2","block3","block4","block5","block6")
  df_wide %>% 
    group_by(learning.condition) %>%
    summarise(block1.mean  = mean(block1, na.rm = T),
              block3.mean = mean(block3, na.rm = T),
              block4.mean = mean(block4, na.rm = T),
              block34.diff = mean((block3-block4)/(block4+block3), na.rm = T),
              block34.se  = sqrt(var((block3-block4)/(block4+block3), na.rm = T)/sum(!is.na(block3-block4))),
              block14.diff = mean((block1-block4)/(block1+block4), na.rm = T),
              block14.se = sqrt(var((block1-block4)/(block1+block4), na.rm = T)/sum(!is.na(block1-block4)))
  )
}
```
 There will be smaller spatial knowledge transfer in those conditions which use less

## Hypotheses
1. There will be some transfer in all learning conditions.
2. Transfer will be higher in the real world learning condition than in desktop treadmill condition.
3. Transfer will be higher in the real world learning condition than in VR treadmill condition.
4. Transfer will be higher in the VR treadmill condition that in the desktop condition.

- transfer is operationalised as a change in performance in navigational tasks following the environment/modality switch
- navigational performance change can be measured in different ways

Specific tests (hypothesis in parenthesis)
- Overrall average walking performance in phase 1 vs phase 2 
- Performance in block 4 vs performance in block 1 and 2

- Overrall average pointing performance in phase 1 vs phase 2 
- Average walking perfomrance in block 3 vs 4 (block directly before vs directly after the switch)
- Personal walking performance change in block 3 vs 4 (calculated as an average of individuals (block3-block4)/(block3+block4))
- Personal walking performance change in block 1 vs 4 (calculated as an average of individuals (block1-block4)/(block3+block4))
- level of correlation of personal performance in block 1,2,3 and 4 - higher transfer should show higher correlation in these comparisons
- Difference in performance between groups in blocks 5 and 6 (e.g. not immediately after the switch, but after all groups have been subjected the real world environment for some time)
- Difference in performance between groups in block 4-6 with inclusion of VR-VR group nad real-VR group (to see if the final performance is subjected to the necessity of a real world experience, or not and to see if the swith has detrimental effect on real-VR as well).

## Controlling analyses
1. Every condition starts on a same level of performance (there isn't a bias in the first block)

## Procedure description
I ran all tests on the normalised distance, errors are not normalised, as they are the same in all conditions.

I only selected those "important" comparisons - therefore Desktop to Real world, Treadmill VR to real world and Real world to real world. Anovas and other comparisons are run only on these. Learning conditions (block 1-3) are the different modalities, and blocks 4-6 are all real world testing.

## Descriptives
In normalised distance we can see that people in different conditions start fairly at the same level of performance (difference between learnign conditions is not significant `r apa_print(aov(min_norm_distance ~ learning.condition, sub_walk_all[sub_walk_all$exp_block_id == 1, ]))$statistic$learning_condition`). Nor there is significant difference between all 5 starting groups `r apa_print(aov(min_norm_distance ~ learning.condition, sub_walk_all[sub_walk_all$exp_block_id == 1, ]))$statistic$condition`.

```{r, echo=F, warning=F}
make_graph(sub_walk_all, "learning.condition", "min_norm_distance", "exp_block_id") + 
  ylab("Average normalised trial distance") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal,"Block ID")

ggplot(sub_walk_all, aes(x = exp_block_id, y = min_norm_distance, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 3.5, linetype=4) +
  ylab("Average normalised trial distance") + xlab("Block") + 
  scale_color_manual(values=estimote_pal,"Condition") + guides(fill=F)
```

There is difference in normalised times in all conditions in the first block (`r apa_print(aov(min_norm_time ~ learning.condition, sub_walk_all[sub_walk_all$exp_block_id == 1, ]))$statistic$learning_condition`)). Probably due to learning issues with the treadmill. Threre is no significant difference between desktop and real world learning in normalised times (`r apa_print(t.test(min_norm_time ~ learning.condition, sub_walk_all[sub_walk_all$exp_block_id == 1 & sub_walk_all$learning.condition %in% c("Desktop", "Real"), ]))$statistic`))

```{r, echo=F}
make_graph(walk_all, "condition", "min_norm_time", "exp_block_id")+ 
  ylab("Average normalised trial duration") + xlab("condition") + 
  scale_fill_manual(values=estimote_pal, "Block ID")
```

And we don't have any significant difference in number of errors in the first block (`r apa_print(aov(errors ~ learning.condition, sub_walk_all[sub_walk_all$exp_block_id == 1, ]))$statistic$learning_condition`)) nor for the all 5 condition (`r apa_print(aov(errors ~ condition, walk_all[walk_all$exp_block_id == 1, ]))$statistic$condition`).

```{r, echo=F}
make_graph(walk_all, "condition", "errors", "exp_block_id")+ 
  ylab("Average number of errors") + xlab("Condition") + 
  scale_fill_manual(values=estimote_pal," Block ID")

ggplot(sub_walk_all, aes(x = exp_block_id, y = errors, color = factor(learning.condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  geom_vline(xintercept = 3.5, linetype=4) +
  ylab("Number of mistakes in office decision") + xlab("Block number") + 
  scale_color_manual(values=estimote_pal, "Condition")
```

## Specific predictions testing

### Performance in block 4 is better than in block 1 and 2
If we assume some level of transfer, than the average or individual performance in block 4 should be better in all conditions than in block 1 or potentially in block 2. I don't test for block 3 because that immediately compares the switch performance. 
```{r, echo=F}
df_dist <- block_t_test(sub_walk_all, 1, 4,"min_norm_distance")[,c(1,4)]
df_error <- block_t_test(sub_walk_all, 1, 4,"errors")[,c(1,4)]
df14 <- merge(df_dist, df_error, by = "learning.condition")
colnames(df14) <- c("learning condition", "p-value distance improvement", "p-value errors improvement")
kable(df14, caption="Paired T test comparing infividual performance improvement from block 1-4 in different conditions")
```
We see taht both real world and treadmill VR learning leads to improvement from block 1 to block 4 in both errors and path travelled. But desktop only in number of errors and marginally in distance improvement.

### Overrall average walking performance in phase 1 vs phase 2
Given that all participants had 3 blocks of trials in the second phase done in the real world, We can assume, if one learning method leads to better transfer than another
```{r, echo=F}

@@

### Overrall average pointing performance in phase 1 vs phase 2
```{r, echo=F}

```
### Average walking perfomrance in block 3 vs 4 
(block directly before vs directly after the switch)
```{r, echo=F}

### Average walkkig perfomance in block 1 vs 4 
(starting baseline vs switch)
```{r, echo=F}

### Personal walking performance change in block 3 vs 4 
(calculated as an average of individuals (block3-block4)/(block3+block4))
```{r, echo=F}

### Personal walking performance change in block 1 vs 4 
(calculated as an average of individuals (block1-block4)/(block3+block4))
```{r, echo=F}

### level of correlation of personal performance in block 1,2,3 and 4

- higher transfer should show higher correlation in these comparisons
```{r, echo=F}

POtential followups
### difference in performance between groups in blocks 5 and 6

(e.g. not immediately after the switch, but after all groups have been subjected the real world environment for some time)
```{r, echo=F}

```
### difference in performance between groups in block 4-6 with inclusion of VR-VR group nad real-VR group

(to see if the final performance is subjected to the necessity of a real world experience, or not and to see if the swith has detrimental effect on real-VR as well).
```{r, echo=F}

@@

clean_walk_14 <- ez_prepare_block(sub_walk_all, c(1,4))
clean_walk_34 <- ez_prepare_block(sub_walk_all, c(3,4))
```
## Block improvement from block 1 to block 4

@@

```{r, echo=F}
df_dist <- block_t_test(sub_walk_all, 3, 4,"min_norm_distance")[,c(1,4)]
df_error <- block_t_test(sub_walk_all, 3, 4,"errors")[,c(1,4)]
df34 <- merge(df_dist, df_error, by = "learning.condition")
colnames(df34) <- c("learning.condition", "p-value distance improvement", "p-value errors improvement")
kable(df34)
```
